Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-15 text/paper2/ms.tex
x to r

\section{Simulations}\label{sec:sims}

We [...] N-body simulations run with an SCF code [...]. [KVJ: describe simulations here?] [Describe tub]

@@

In \paperone, we define a set of coordinates relative to the instantaneous phase-space position of the progenitor, $(\bs{x}_{p},\bs{v}_{p})$, normalized by the instantaneous tidal radius and escape velocity. Here we (1) scale the velocity coordinates by the velocity dispersion of the satellite instead of the escape velocity, (2) reduce the dimensionality by considering only the magnitude of these vectors, and (3) take the logarithm of the magnitude,
\begin{equation}
  R = \ln\left(\frac{\left\vert\bs{x} - \bs{x}_{p}\right\vert}{R_{\rm tide}}\right)\,\,\,\,,\,\,\,\,
  V = \ln\left(\frac{\left\vert\bs{v} - \bs{v}_{p}\right\vert}{\sigma_v}\right).
\end{equation}

>>>>

\section{Simulations}\label{sec:sims}
[David H.]
We [...] N-body simulations run with an SCF code [...]. [describe simulations here] [Describe tub]

@@

In \paperone, we define a set of coordinates relative to the instantaneous phase-space position of the progenitor, $(\bs{r}_{p},\bs{v}_{p})$, normalized by the instantaneous tidal radius and escape velocity. Here we (1) scale the velocity coordinates by the velocity dispersion of the satellite instead of the escape velocity, (2) reduce the dimensionality by considering only the magnitude of these vectors, and (3) take the logarithm of the magnitude,
\begin{equation}
  R = \ln\left(\frac{\left\vert\bs{r} - \bs{r}_{p}\right\vert}{R_{\rm tide}}\right)\,\,\,\,,\,\,\,\,
  V = \ln\left(\frac{\left\vert\bs{v} - \bs{v}_{p}\right\vert}{\sigma_v}\right).
\end{equation}
